The first high-redshift Changing Look Quasars

### 2019-11-07 tex/other_tex/olderthan_201909/CIV_notes_20190820.tex
CIV tex/ tidy up

\author[Bercow]
{The RH John~S.~Bercow, MP, {\it et al.} 
%Nicholas~P.~Ross$^{1}$\thanks{E-mail: npross@roe.ac.uk},    
% Matthew Graham$^{5}$
% K. E. Saavik Ford$^{2,3,4}$, 
% Barry McKernan$^{2,3,4}$,  
%\newauthor Daniel Stern$^{6}$, 
\\
%% List of institutions
$^{1}$Speaker's Chair, The House of Commons, London, SW1A 0AA \\
%$^{1}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, United Kingdom \\
%$^{2}$Department of Science, BMCC, City University of New York, New York, NY 10007, USA \\
%$^{3}$Department of Astrophysics, Rose Center for Earth and Space, American Museum of Natural History, Central Park West at 79th Street, NY 10024, USA \\
%$^{4}$Graduate Center, City University of New York, 365 5th Avenue, New York, NY 10016, USA\\
%$^{5}$Cahill Center for Astronomy and Astrophysics, California Institute of Technology, Mail Code 249/17, 1200 E California Blvd, Pasadena CA 91125, USA\\
%$^{6}$Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Mail Stop 169-221, Pasadena, CA 91109, USA \\
}

\date{Accepted XXX. Received YYY; in original form ZZZ}
\pubyear{2019}

@@

\begin{abstract}
%% 190 words of 'lorem ipsum' (200 words Abstract total for MNRAS Letters)
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Nunc imperdiet facilisis volutpat. Phasellus ultricies justo a ante bibendum porta. Nulla varius convallis risus in tincidunt. Vivamus sit amet massa non dui volutpat porttitor. Donec imperdiet mauris non risus commodo tempor. Nulla volutpat nulla a lorem lobortis, a luctus nulla rhoncus. Vestibulum vel ante elementum nisl feugiat sollicitudin. Aenean purus sem, mattis vitae odio et, varius vehicula nulla.
%%
Nulla ante mauris, mattis a tristique eu, pharetra eget erat. Cras et ultrices lectus. Praesent augue erat, commodo ac malesuada vel, mattis ac nisi. Quisque eu vehicula urna, in fringilla nunc. Duis faucibus scelerisque felis, sollicitudin luctus tortor pretium dapibus. Sed cursus scelerisque dapibus. Proin a bibendum neque, sit amet aliquet arcu. Vivamus in eros lectus. Nam dui felis, convallis sit amet dolor ut, dignissim posuere nunc. Donec egestas tellus vel urna interdum tincidunt. Sed orci eros, convallis in rhoncus sit amet, tincidunt ac est. Mauris tempus, diam a euismod tempus, est turpis laoreet justo, quis posuere augue ipsum sed nisi. Aliquam non lobortis tellus. Morbi vulputate porta placerat. Quisque dapibus pretium arcu eget tempor. Aenean in tincidunt nisi. Aenean interdum congue enim.
\end{abstract}

@@

%% \subsection{Literature Search}

@@

\citet{Wilhite2005} and especially \citet{Wilhite2006}

\citet{Wilhite2008} also...

@@

%%\subsection{Carbon IV}
Table~\ref{tab:civ_configs} from 
Atomic Line List version: 2.05b21  
%%Version 2.05b21 of the line list was created: Nov 7, 2017.
\citep{Tunklev1997} \\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/J2228+2201.png}
  \vspace{-12pt}
  \caption[]{J222818.7+220102.6. 
% EMERGING., 
The light curve shows it brightening from 20.5 to 19.5 over the 771 days observed-frame between the two SDSS spectra available. 
A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] emerging on a new blue contiuum slope.}
  \label{fig:disk_suppression}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/J1638+2827.png}
  \vspace{-12pt}
  \caption[]{The quasar SDSS J163852.9+282708. 
% Disappearing 
A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] fading.}
  \label{fig:disk_suppression}
\end{figure}
\section{Data}
\subsection{Selection/Identification}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
Even with nearly a change of a decade in the continuum flux, no 
no change is seen in the flux of the \civ line flux \citet[e.g. Figure 6 in ][]{Hawkins2011}.

\citep{Wilhite2006} for SDSS...

\subsection{In the context of CLQs at lower-$z$}

>>>>

\author[Bercow]
{The RH John~S.~Bercow, MP, {\it et al.} 
%Nicholas~P.~Ross$^{1}$\thanks{E-mail: npross@roe.ac.uk},    
%K. E. Saavik Ford$^{2,3,4}$,  Matthew Graham$^{5}$,  Barry McKernan$^{2,3,4}$,  
%\newauthor Daniel Stern$^{6}$, 
%Aaron M. Meisner$^{7,8}$, Roberto J. Assef$^{9}$, Arjun Dey$^{10}$, Andrew J. Drake$^{11}$, \newauthor Hyunsung D. Jun$^{12}$, Dustin Lang$^{13,14,15}
\\
% List of institutions
$^{1}$Speaker's Chair, The House of Commons, London, SW1A 0AA \\
%$^{1}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, United Kingdom \\
%$^{2}$Department of Science, BMCC, City University of New York, New York, NY 10007, USA \\
%$^{3}$Department of Astrophysics, Rose Center for Earth and Space, American Museum of Natural History, Central Park West at 79th Street, NY 10024, USA \\
%$^{4}$Graduate Center, City University of New York, 365 5th Avenue, New York, NY 10016, USA\\
%$^{5}$Cahill Center for Astronomy and Astrophysics, California Institute of Technology, Mail Code 249/17, 1200 E California Blvd, Pasadena CA 91125, USA\\
%$^{6}$Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Mail Stop 169-221, Pasadena, CA 91109, USA \\
}

\date{Accepted XXX. Received YYY; in original form ZZZ}
\pubyear{2018}

@@

\begin{abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Nunc imperdiet facilisis volutpat. Phasellus ultricies justo a ante bibendum porta. Nulla varius convallis risus in tincidunt. Vivamus sit amet massa non dui volutpat porttitor. Donec imperdiet mauris non risus commodo tempor. Nulla volutpat nulla a lorem lobortis, a luctus nulla rhoncus. Vestibulum vel ante elementum nisl feugiat sollicitudin. Aenean purus sem, mattis vitae odio et, varius vehicula nulla.
%%
Nulla ante mauris, mattis a tristique eu, pharetra eget erat. Cras et ultrices lectus. Praesent augue erat, commodo ac malesuada vel, mattis ac nisi. Quisque eu vehicula urna, in fringilla nunc. Duis faucibus scelerisque felis, sollicitudin luctus tortor pretium dapibus. Sed cursus scelerisque dapibus. Proin a bibendum neque, sit amet aliquet arcu. Vivamus in eros lectus. Nam dui felis, convallis sit amet dolor ut, dignissim posuere nunc. Donec egestas tellus vel urna interdum tincidunt. Sed orci eros, convallis in rhoncus sit amet, tincidunt ac est. Mauris tempus, diam a euismod tempus, est turpis laoreet justo, quis posuere augue ipsum sed nisi. Aliquam non lobortis tellus. Morbi vulputate porta placerat. Quisque dapibus pretium arcu eget tempor. Aenean in tincidunt nisi. Aenean interdum congue enim.
\end{abstract}

@@

\subsection{Literature Search}

@@

@@

\subsection{Carbon IV}
Table~\ref{tab:civ_configs} from 
Atomic Line List version: 2.05b21  
%%Version 2.05b21 of the line list was created: Nov 7, 2017.
\citep{Tunklev1997} \\

@@

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/J2228+2201.png}
  \vspace{-12pt}
  \caption[]{J222818.7+220102.6. 
% EMERGING., 
The light curve shows it brightening from 20.5 to 19.5 over the 771 days observed-frame between the two SDSS spectra available. 
A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] emerging on a new blue contiuum slope.}
  \label{fig:disk_suppression}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/J1638+2827.png}
  \vspace{-12pt}
  \caption[]{The quasar SDSS J163852.9+282708. 
% Disappearing 
A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] fading.}
  \label{fig:disk_suppression}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data}
\subsection{Selection/Identification}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\subsection{In the context of CLQs at lower-$z$}

### 2019-11-07 tex/other_tex/olderthan_201909/CIV_notes_20190829.tex
CIV tex/ tidy up

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
While there have been a slew of studies on triply ionized carbon, i.e \civ, broad absorption line quasars
\citep[BAL QSOs; see e.g. Table 1][]{Hemler2019}, dramatic changes in the 
broad {\it emission} line (BEL) of \civ, and indeed, \ciii have not to this point been seen. 
Here, we report on two objects SDSS J222818.76+220102.9 (hereafter J2228+2201) and 
SDSS J163852.93+282707.7 (hereafter J1638+2827) which show dramatic changes in the \civ broad emission line properties, as well as in the underlying continuum. We claim these are the first examples of ``Changing Look Quasars'' at high ($z>1$) redshift and for emission lines with high ionization potentials (I.P.'s 
$>$13.6 eV).

For J2228+2201, over the course of 771 days observed, 240 days in the rest-frame, broad \civ and \ciii BELs both emerge and the
standard UV/blue continuum slope increases in flux. 
For J1638+2827, over the course of 1279 days observed, 400 days in the rest-frame, the  broad \civ and \ciii BEL start to fade, 
the UV/blue continuum diminishes and the shape of \lya changes.

\subsection{Literature Search}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
While there have been a slew of studies on triply ionized carbon, i.e \civ, broad absorption line quasars
\citep[BAL QSOs; see e.g. Table 1][]{Hemler2019}, dramatic changes in the 
broad {\it emission} line (BEL) of \civ, and indeed, \ciii have not to this point been seen. 
%% 
Here, we report on three objects 
SDSS J120544.7+342252.4  (hereafter J1205+3422), 
SDSS J163852.93+282707.7 (hereafter J1638+2827) and
SDSS J222818.76+220102.9 (hereafter J2228+2201)  
which show dramatic changes in the \civ broad emission line
properties, as well as in the underlying continuum. We claim these are
the first examples of ``Changing Look Quasars'' at high ($z>1$)
redshift and for emission lines with high ionization potentials
(I.P.'s $>$13.6 eV).

For J1638+2827, over the course of 1279 days observed, 400 days in the rest-frame, the  broad \civ and \ciii BEL start to fade.  
For J2228+2201, over the course of 771 days observed, 240 days in the rest-frame, broad \civ and \ciii BELs both emerge and the 
standard UV/blue continuum slope increases in flux. 
the UV/blue continuum diminishes and the shape of \lya changes.

\subsection{Literature Search}
\citet{Wilhite2006} examine the variability of the high-ionizaton
C~\textsc{iv}$\lambda{1549}$ line in a sample of 105 quasars observed
at multiple epochs by the Sloan Digital Sky Survey.  We find a strong
correlation between the change in the C~\textsc{iv} line flux and the
change in the line width, but no correlations between the change in
flux and changes in line center and skewness.  The relation between
line flux change and line width change is consistent with a model in
which a broad line base varies with greater amplitude than the line
core. The objects studied here are more luminous and at higher
redshift than those normally studied for variability, ranging in
redshift from 1.65 to 4.00 and in absolute $r$-band magnitude from
roughly $-$24 to $-$28.  Using moment analysis line-fitting
techniques, we measure line fluxes, centers, widths and skewnesses for
the C~\textsc{iv} line at two epochs for each object.  The well-known
Baldwin Effect is seen for these objects, with a slope $\beta =
-0.22$.  The sample has a median intrinsic Baldwin Effect slope of
$\beta_{int} = -0.85$; the C~\textsc{iv} lines in these
high-luminosity quasars appear to be less responsive to continuum
variations than those in lower luminosity AGN.  Additionally, we find
no evidence for variability of the well known blueshift of the
C~\textsc{iv} line with respect to the low-ionization
Mg~\textsc{ii}$\lambda$2798 line in the highest flux objects,
indicating that this blueshift might be useful as a measure of
orientation.

@@

Double Spectrograph (DBSP) is a low-to-medium resolution ($R\sim$1,000
to 10,000) grating instrument for the Palomar 200-inch telescope
Cassegrain focus that uses a dichroic (at, e.g., 5200\AA\ ) to split
light into simultaneously observed separate red and blue channels.

The Low Resolution Imaging Spectrometer (LRIS) is a visible-wavelength
imaging and spectroscopy instrument commissioned in 1993 and operating
at the Cassegrain focus of 10-meter Keck I telescope.

\begin{table*}
 \centering
 \begin{tabular}{r  r  r r    r r r r}
  \hline \hline 
% &&\\
   Object                          & Redshift  & Mag       & Date                               & Instrument    & Exp. Time            & Spectrum & Notes \\
% &&\\
 \hline 
                                       &                &               &                                         &                   &                             &  & \\
   J120544.7+342252.4   & 2.071     &   17.99   & 53498  (2005-May-08)   & SDSS             & ?                          & 53498-2089-427  & \\
                                       &                &               & 58538 (2019-Feb-24)     & DBSP            &  2$\times$900    &                               &  Conditions? \\
                                       &                &               & 58693 (2019-Jul-29)      & DBSP            &  2$\times$1200   &                                &   \\
                                       &                &               &                                         &                   &                             &  & \\
   J163852.9+282707.7   & 2.182     &   19.77    & 54553 (2008-Mar-28)    & SDSS             & ?                          & 54553-2948-614  & \\
                                        &               &              & 55832  (2011-Sep-28)     & BOSS            &   3603                  & 55832-5201-178  & \\
                                        &               &              & 58583 (2019-Apr-10)        & LRIS              &  2$\times$900    &   & \\
                                       &                &               &                                         &                   &                             &  & \\
    J222818.7+220102.9   & 2.222     & 19.97    & 56189  (2012-Sept-19)     & BOSS             &  2702               & 56189-6118-720   & \\
                                         &              &              & 56960   (2014-Oct-30)    & BOSS             & ?                         & 56960-7582-790     & QSO1-REOBS \\ 
                                         &               &             & 58693 (2019-Jul-29)      & DBSP              & 2$\times$1200  &       &    \\
                                       &                &               &                                         &                   &                             &  & \\
   \hline \hline   
  \end{tabular}
  \caption{Spectrum is SDSS/BOSS MJD-Plate-FiberID combination. 
Exposure times are from the {\tt plate.fits} file. 
DBSP on the Palomar 200-inch telescope is the } 
 \label{tab:obs_notes}
\end{table*}
